\chapter{Summary and Conclusions} \label{conclusion}

\section{Summary}
This report described the conceptual design of the B\&B platform \textit{Room.io}, from gathering initial requirements to defining use cases, specifying necessary sequences and classes up to laying out a plan for implementation and providing mock ups of the final product.

\section{Conclusions}

This project neatly drew upon the group's knowledge and skills acquired in other course modules. A prior App Design project had introduced the group to human computer interaction which was applied in identifying the requirements and formulating the use cases for the proposed System. Both App Design and Database modules provided the background to anticipate how the service would be hosted, together with the likely front and back end functionality. The database module in particular provided the necessary insight into the requirements in terms of the likely database schema and how the Users would interact with this. Existing object-orientated programming knowledge helped hone the design in a way that would facilitate the implementation of the system. All of this background was invaluable in putting together the illustrations, tables and diagrams that formed the overall design. A great part of the success of the project, was, however, attributable to the team work involved. The group met as a whole on Friday mornings and Monday afternoons. Monday was the opportunity to divide up tasks for the coming few days and was at times followed by a conversation with Graham Roberts to clarify any points that had arisen over the weekend. On fridays, the group caught up and seized the opportunity to update their supervisor, Rae Harbird. Between these meetings, issues were discussed over Slack channel and in informal sub-team meetings. These sub-teams established the first draft of the requirements and use cases. The group as a whole refined these as they moved further into the analysis and design stages. At the conclusion of the project, a system had been designed that had been considered from many possible angles and that satisfied the requirements identified in the beginning. As a consequence, the group is confident that they laid the foundation for the robust and effective B\&B Booking system that they set out to design.

\section{Who Did What}
Aleksi took on a valuable overview role for much of the project, helping to ensure coherence between different diagrams and correct application of the theory in this context. Other members of the group assisted Aleksi in reviewing output through git hub and Slack postings. Each week there was considerable Slack traffic between all group members with comments on consistency, suggested revisions and updates on tasks. Zaid, with a Software Engineering background, was a useful sounding board when there were queries about the design features for our system. This was very much a whole team project. As indicated above, the formulation of the requirements, use cases and the diagrams involved all group members, although sub-teams initially focused on specific actors in the process. The final outcome was ultimately down to the fact that each team member was fully committed to the task and to delivering a high quality project. For an overview on the individual responsibilities of each group member, please see Table \ref{contribution}.



    \begin{table}[H]
        \centering
        \footnotesize
        \begin{tabular}{| w | p{12cm}@\qquad |}
          \hline
          Aleksi Anttila & Overall cohesiveness and consistency co-ordination; primary responsibility for use cases, sequence diagrams and glossary (setting templates, keeping track of changes and finalising); set up report outline; \LaTeX helper\\ \hline

          Michael Aring & Requirements list, use cases, initial sub-group for Host requirements, drafting related sections of report, project management, analysis class diagram, sequence diagram, video production  \\ \hline

          Kai Klasen & Use cases, analysis class diagram, sequence and activity diagrams initial sub-group for Guest requirements etc, drafting relating sections of report, video narrator  \\ \hline

          Lorenz Luboldt & Requirements list, use cases, activity diagrams, class diagrams, initial sub-group for Host requirements/use cases, state machine diagram, drafting related sections of report, video production   \\ \hline

          Christina Kronser & Preparation of meeting agendas, requirements lists, use case tables, class diagrams, sequence and activity diagrams, mockups, initial sub group for Guest requirements/use cases, state machine diagram, video production \\ \hline

          Philip Spencer & Requirements list, use cases, activity diagrams, initial sub-group for Host requirements/use cases, drafting scope and vision document, draft of report abstract and conclusion, draft video script, meeting liaison.  \\ \hline

          Paul Venhaus & Overall monitoring of requirements, use cases, introduction to report including domain model and gantt chart, component and deployment diagrams, initial sub-group focusing on Guest requirements/use cases, video production, and \LaTeX superuser \\ \hline

          Zaid Al Lahham & Analysis and Design class diagram, requirements list, use cases, component and deployment diagrams, initial sub-group to focus on Admin requirements, video production, and \LaTeX superuser   \\ \hline
        \end{tabular}
        \caption{Team Contribution}
        \label{contribution}
      \end{table}
 