\begin{abstract}

This project report covers the processes involved in the design of the web-based software system \textit{Room.io}, serving the Bed and Breakfast (B\&B) industry in the UK. It is accompanied by a video showing the system design. The objective has been to design the system up to the point where it could be passed across to a development team for implementation.

The system described in this work allows B\&B owners to register properties, to advertise them, and to accept bookings from users. Guests are able to search for properties along different dimensions and complete bookings in the software.

The report commences with the vision and scope of the project. The following chapters cover the design stages starting with the identification of the system requirements and then progressively drilling down into the use cases together with the system analysis class diagram.   

Following the analysis stage, the report moves on to considering the object-oriented design phase where key interactions and activities are illustrated through sequence, activity, and state machine diagrams. A design class diagram is presented based on the analysis class diagram. It further includes methods and attributes in the various classes that provide guidance on implementation issues that the implementing developers will need to address. The report also includes component and deployment diagrams that show the intended interaction between hardware and software components.

The role and theory in relation to the various stages and related diagrams have been commented upon in the relevant sections. 

The report ends with a conclusion and reflection on the project.

\end{abstract}